---
title: "IAMB_dev_ws"
output: html_notebook
---

Ultilizing the IAMB feature in bnlearn package to learn the structure of a Bayesian Network.
Install packages
```{r}
install.packages(`bnlearn`)
install.packages("BiocManager")
BiocManager::install("Rgraphviz")
```

Import them into the current R session
```{r}
library(bnlearn)
library(Rgraphviz)
```

Opens a file chooser dialog box for the user to select a file. 
The selected file's path is then assigned to the variable `path_lsds_15`.
Reads the CSV file specified by the `path_lsds_15` variable into a data frame named `data_lsds_15`.
The `read.csv()` function is used to read CSV files, and the `header=FALSE` argument indicates that the file does not have a header row. The `skip=1` argument skips the first line of the file.
```{r}
path_lsds_15 <- file.choose()
data_lsds_15 <- read.csv(path_lsds_15, header=FALSE, skip=1)
```

Removes the first column from the `data_lsds_15` data frame. 
The `subset()` function is used to extract a subset of the data frame, and the `select=-(1:1)` argument specifies to remove the first column. 
The minus sign (`-`) indicates removal.
Then prints the contents of the `data_lsds_15` data frame
```{r}
data_lsds_15 <- subset(data_lsds_15, select=-(1:1))
data_lsds_15
```

Applies the `iamb()` function from the `bnlearn` package to learn the structure of a Bayesian network
```{r}
dag <- bnlearn::iamb(data_lsds_15)
```

Converts the learned Bayesian network structure into a graphNEL object.
The resulting graph is stored in the `graph_dag` object which will be plotted
```{r}
graph_dag <- bnlearn::as.graphNEL(dag)
plot(graph_dag)
```
